\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-10-21 main.tex

\begin{figure}[!h]
\centering
\begin{subfigure}{.235\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_currents.png}
  \caption{Uniform applied field.}
  \label{fig:circular_ring_plot_currents}
\end{subfigure}
\begin{subfigure}{.235\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_fields.png}
  \caption{Uniform applied field.}
  \label{fig:circular_ring_plot_fields}
\end{subfigure}
\begin{subfigure}{.235\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_currents.png}
  \caption{Trapped flux.}
  \label{fig:square_ring_plot_currents}
\end{subfigure}
\begin{subfigure}{.235\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_fields.png}
  \caption{Trapped flux.}
  \label{fig:square_ring_plot_fields}
\end{subfigure}

\caption{Sheet current $\vec{J}$ (a, c) and magnetic field $\mu_0H_z$ (b, d) distributions for the circular ring with a uniform field of 0.25 mT applied out-of-plane (a, b) and a circulating current of 1 mA (c, d) calculated using Code Block~\ref{code:ring_circulating_current}.}
\label{fig:ring_plot_fields_currents}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{examples/images/square_ring_results.png}
    \caption{Caption}
    \label{fig:square-ring-results}
\end{figure}

% \begin{figure}[!h]
% \centering
% \begin{subfigure}{.235\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_currents.png}
%   \caption{Uniform applied field.}
%   \label{fig:circular_ring_plot_currents}
% \end{subfigure}
% \begin{subfigure}{.235\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_fields.png}
%   \caption{Uniform applied field.}
%   \label{fig:circular_ring_plot_fields}
% \end{subfigure}
% \begin{subfigure}{.235\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_currents.png}
%   \caption{Trapped flux.}
%   \label{fig:square_ring_plot_currents}
% \end{subfigure}
% \begin{subfigure}{.235\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_fields.png}
%   \caption{Trapped flux.}
%   \label{fig:square_ring_plot_fields}
% \end{subfigure}

% \caption{Sheet current $\vec{J}$ (a, c) and magnetic field $\mu_0H_z$ (b, d) distributions for the circular ring with a uniform field of 0.25 mT applied out-of-plane (a, b) and a circulating current of 1 mA (c, d) calculated using Code Block~\ref{code:ring_circulating_current}.}
% \label{fig:ring_plot_fields_currents}
% \end{figure}
